---
title: "Monthly Storage Report"
output:
  html_document:
    smart: false 
---

```{r, warning=FALSE, include=FALSE}
#loading libraries
library(tidyverse)
library(gt)
library(osfr)
library(lubridate)
library(here)
library(plotly)
library(DT)

options(digits=10)

# creating additional variables
storage_data <- read_csv(paste0(here::here('Data_Usage/'), 'osf_storage_metrics.csv'), col_types = cols(date = col_datetime())) %>%
                    mutate(date = rollback(date, roll_to_first = FALSE)) %>%
                    mutate(month = month(date, label = T),
                    year = year(date)) %>%
                    mutate(total = case_when(date > '2020-08-31' ~ total - deleted,
                                             TRUE ~ total),
                           deleted = case_when(date > '2020-08-31' ~ 0,
                                             TRUE ~ deleted)) %>%
                    mutate(total_tib = round(total/(1024^3),2),
                           deleted_tib = round(deleted/(1024^3),2),
                           regs_tib = round(registrations/(1024^3),2),
                           quickfiles_tib = round(nd_quick_files/(1024^3),2),
                           pubnode_tib = round(nd_public_nodes/(1024^3),2),
                           privatenode_tib = round(nd_private_nodes/(1024^3),2),
                           node_tib = round((nd_public_nodes + nd_private_nodes)/(1024^3),2),
                           preprint_tib = round(nd_preprints/(1024^3),2),
                           suppnode_tib = round(nd_supp_nodes/(1024^3),2),
                           prct_del = 100*(deleted/total),
                           prct_regs = 100*(registrations/total),
                           prct_quickfiles = 100*(nd_quick_files/total),
                           prct_preprints = 100*(nd_preprints/total),
                           prct_pub_nodes = 100*(nd_public_nodes/total),
                           prct_pri_nodes = 100*(nd_private_nodes/total))

# download and readin monthly cap info
osf_retrieve_file('https://osf.io/dpe2j/') %>%
  osf_download(path = here::here('Data_Usage/'), conflicts = "overwrite")

monthly_cap_info <- read_csv(paste0(here::here('Data_Usage/'), 'monthly_cap_info.csv'))
```

```{r, warning=FALSE, include=FALSE}

# create public & private storage counts by root_id of non-deleted files and nodes
by_node_storage <- read_csv(paste0(here::here('Data_Usage/'), 'nondel_nodedata.csv'), col_types = cols(deleted_on = col_skip(),
                                                                  target_object = col_skip(),
                                                                  target_type = col_skip(),
                                                                  target_is_fork = col_skip(),
                                                                  target_is_deleted = col_skip())) %>%
                 group_by(target_guid, target_is_public, target_root) %>%
                 summarize(tot_size = sum(size)) %>%
                 mutate(gig_tot_size = round(tot_size/(1024^3),3))
                 
```


#### Total storage increased by `r round(100 * (storage_data$total[nrow(storage_data)]/storage_data$total[nrow(storage_data) - 1]) - 100,2)`% this month.

The data used to generate this report can be found [here](https://osf.io/a7w36/). 

```{r, warning=FALSE, include=FALSE}
### creating data formatted for tables

# create all difference variables
storage_dt <- storage_data %>%
                      filter(date >= as.Date(Sys.time()) - dyears(1)) %>%
                      select(date, month, total_tib, pubnode_tib, privatenode_tib, deleted_tib, node_tib, preprint_tib, quickfiles_tib, regs_tib) %>%                    
                      mutate_if(is.numeric, funs(diff = . - lag(.))) %>%
                      filter(date >= as.Date(Sys.time()) - months(9)) %>%
                      select(-date) %>%
                      column_to_rownames('month')
                      
                      

# transpose dataframe
transpose_storage <- data.table::transpose(storage_dt)
rownames(transpose_storage) <- colnames(storage_dt)
colnames(transpose_storage) <- rownames(storage_dt)

#reformat product names
transpose_storage <- transpose_storage %>%
                          rownames_to_column() %>%
                          rename(Type = rowname) %>%
                          mutate(Type = case_when(grepl('total_tib', Type) ~ 'Total',
                                    grepl('deleted_tib', Type) ~ 'Deleted',
                                    grepl('pubnode_tib', Type) ~ 'Public Nodes',
                                    grepl('privatenode_tib', Type) ~ 'Private Nodes',
                                    grepl('node_tib', Type) ~ 'Nodes',
                                    grepl('regs_tib', Type) ~ 'Registrations',
                                    grepl('preprint_tib', Type) ~ 'Preprints',
                                    grepl('quickfiles_tib', Type) ~ 'Quickfiles'))
```

\
\
\


```{r, warning=FALSE, echo=FALSE}
# overall storage
transpose_storage %>% 
  filter(Type == 'Total' | Type == 'Public Nodes' | Type == 'Private Nodes') %>%
  gt() %>%
  cols_align(align = c('center')) %>%
  tab_header(
    title = 'Overall Storage'
  ) %>%
  tab_row_group(
    group = 'Monthly Total',
    rows = 1:3
  ) %>%
  tab_row_group(
    group = 'Monthly Increase',
    rows = 4:6
  ) %>%
  tab_source_note(
    source_note = "Storage displayed in Gigabytes"
  ) %>%
  tab_footnote(
    footnote = 'Includes preprint supp nodes',
    locations = cells_data(
      columns = vars(Type),
      rows = c(2, 5)
    )
  ) %>%
  tab_footnote(
    footnote = 'After consult with product, no deleted files [even ones > 30 days old] included in total starting 9/20. Before 9/20, deleted storage is included in Total, but not listed in the table',
    locations = cells_data(
      columns = vars(Type),
      rows = c(1, 4)
    )
  )


```

\
\
\

```{r, warning=FALSE, echo=FALSE}
# monthly storage
transpose_storage %>% 
  filter(Type == 'Nodes' | Type == 'Registrations' | Type == 'Preprints' | Type == 'Quickfiles') %>%
  gt() %>%
  cols_align(align = c('center')) %>%
  tab_header(
    title = 'Storage by Product'
  ) %>%
  tab_row_group(
    group = 'Monthly Total',
    rows = 1:4
  ) %>%
  tab_row_group(
    group = 'Monthly Increase',
    rows = 5:8
  ) %>%
  tab_source_note(
    source_note = "Storage displayed in Gigabytes"
  ) %>%
  tab_footnote(
      footnote = 'Includes preprint supp nodes',
      locations = cells_data(
        columns = vars(Type),
        rows = c(1, 5)
      )
    ) %>%
   tab_footnote(
        footnote = 'Excludes preprint supp nodes',
        locations = cells_data(
          columns = vars(Type),
          rows = c(2, 6)
        )
      )
```


```{r, warning=FALSE, echo=FALSE}
# formatting data for graph
data_graph <- storage_data %>%
  select(date, starts_with('prct')) %>%
  gather(prct_del:prct_pri_nodes, key = 'storage_type', value = 'perc_of_total', factor_key = T) %>%
  mutate(perc_of_total = round(perc_of_total, 2))
  

data_graph$storage_type <- fct_recode(data_graph$storage_type, Quickfiles = 'prct_quickfiles',
                                    Registrations = 'prct_regs',
                                    `Public Nodes` = 'prct_pub_nodes',
                                    `Private Nodes` = 'prct_pri_nodes',
                                    `Deleted Content` = 'prct_del',
                                    Preprints = 'prct_preprints')
data_graph$storage_type <- fct_relevel(data_graph$storage_type, c('Public Nodes', 'Private Nodes', 'Preprints', 'Quickfiles', 'Registrations', 'Deleted Content'))
```

\
\
\

```{r, warning=FALSE, echo=FALSE}
# graph of monthly storage by percent
graph  <- plot_ly(data_graph, x = ~date, y = ~ perc_of_total, color =  ~storage_type, colors='Spectral',
                       type = 'scatter', mode = 'line') %>%
                layout(xaxis = list(title = "",
                                    nticks = nrow(storage_data),
                                    tickformat = '%b %y'),
                       yaxis = list(title = "Percentage of Total Storage"))

graph


```

\
\
\

```{r, warning=FALSE, echo=FALSE, message = FALSE}
# num/perc of nodes/projects by type and month:

month <- floor_date(as_datetime(Sys.time()), 'months') - days(1)

num_public_above <- nrow(by_node_storage %>% 
        filter(target_is_public == TRUE & gig_tot_size >= 50))

num_private_above <- nrow(by_node_storage %>% 
        filter(target_is_public == FALSE & gig_tot_size >= 5))

perc_public_nodes <- round(100 * nrow(by_node_storage %>% 
        filter(target_is_public == TRUE))/nrow(by_node_storage),2)

perc_private_nodes <- 100 - perc_public_nodes

perc_public_above <- round(100 * nrow(by_node_storage %>% 
        filter(target_is_public == TRUE & gig_tot_size >= 50))/nrow(by_node_storage %>% 
        filter(target_is_public == TRUE)),2)

perc_public_above_5GB <- round(100 * nrow(by_node_storage %>% 
        filter(target_is_public == TRUE & gig_tot_size > 5))/nrow(by_node_storage %>% 
        filter(target_is_public == TRUE)),2)

perc_private_above <- round(100 * nrow(by_node_storage %>% 
        filter(target_is_public == FALSE & gig_tot_size >= 5))/nrow(by_node_storage %>% 
        filter(target_is_public == FALSE)),2)

perc_toplevel_public_above <- round(100 * (by_node_storage %>% 
        filter(target_is_public == TRUE) %>%
        group_by(target_root) %>%
        summarise(num_nodes = n(), gig_tot_size = sum(gig_tot_size)) %>%
        filter(num_nodes > 1 & gig_tot_size >= 50) %>%
        nrow())/(by_node_storage %>% 
        filter(target_is_public == TRUE) %>%
        group_by(target_root) %>%
        summarise(num_nodes = n(), gig_tot_size = sum(gig_tot_size)) %>%
        filter(num_nodes > 1) %>%
        nrow()),2)

perc_toplevel_private_above <- round(100 * (by_node_storage %>% 
        filter(target_is_public == FALSE) %>%
        group_by(target_root) %>%
        summarise(num_nodes = n(), gig_tot_size = sum(gig_tot_size)) %>%
        filter(num_nodes > 1 & gig_tot_size >= 5) %>%
        nrow())/(by_node_storage %>% 
        filter(target_is_public == FALSE) %>%
        group_by(target_root) %>%
        summarise(num_nodes = n(), gig_tot_size = sum(gig_tot_size)) %>%
        filter(num_nodes > 1) %>%
        nrow()),2)

# append this monthsly numbers onto running sheet and uplaod back to osf
this_months_cap_info <- cbind(month, num_public_above, num_private_above, perc_public_nodes, perc_private_nodes, perc_public_above, perc_public_above_5GB, perc_private_above, perc_toplevel_public_above, perc_toplevel_private_above) %>%
  as.data.frame() %>%
  mutate(month = as_datetime(month))

monthly_cap_info <- rbind(monthly_cap_info, this_months_cap_info)

write_csv(monthly_cap_info, 'monthly_cap_info.csv')

osf_retrieve_node('https://osf.io/r83uz/') %>% 
  osf_ls_files() %>% 
  filter(name == 'Data Storage Usage') %>%
  osf_upload(path = here::here('Data_Usage/monthly_cap_info.csv'), conflicts = "overwrite")

```



# Storage Cap Information

### How many nodes are exceeding the caps?
```{r, warning=FALSE, echo=FALSE}
storage_fig <- monthly_cap_info %>%
  select(month, num_public_above, num_private_above, perc_public_above, perc_private_above) %>%
  mutate(num_private_above = num_private_above - monthly_cap_info[1, 3][[1]],
         num_public_above = num_public_above - monthly_cap_info[1, 2][[1]]) %>%
  pivot_longer(!month, names_to = c('type','Node Type', 'placement'), 
               names_sep = '_',
               values_to = 'value') %>%
  select(-placement) %>%
  mutate(type = case_when(type == 'num' ~ 'Change in number of nodes since Nov 2020',
                          type == 'perc' ~ 'Percentage of nodes'),
         month = as.Date(month)) %>%
  ggplot(aes(x = month, y = value, color = `Node Type`)) +
    geom_line() +
    geom_point() + 
    theme_minimal() + 
    theme(axis.title = element_blank()) + 
    facet_wrap( ~ type, ncol = 1, scales="free_y") +
    scale_x_date(date_labels = "%b %y")

ggplotly(storage_fig)
```

#### Other General Numbers
* Overall percentage of private nodes: `r perc_private_nodes`%
* Overall percentage of public nodes: `r perc_public_nodes`%
* Percentage of public nodes above private cap: `r perc_public_above_5GB`%


### Are users getting around the cap by creating nested projects?

If there is an unexpectedly large incrase in node storage, but not a spike in projects getting around the node caps, it could be that a large number of individual projects were made, which would show up in the KPIs, or that users have switched to more nested projects to spread files to multiple nodes to get around caps. 

```{r, warning=FALSE, echo=FALSE}
nested_storage_fig <- monthly_cap_info %>%
  select(month, perc_toplevel_public_above, perc_toplevel_private_above) %>%
  pivot_longer(!month, 
               names_to = 'Node Type', 
               values_to = 'Percentage') %>%
  mutate(`Node Type` = case_when(`Node Type` == 'perc_toplevel_public_above' ~ 'public',
                          `Node Type` == 'perc_toplevel_private_above' ~ 'private'),
         month = as.Date(month)) %>%
  ggplot(aes(x = month, y = Percentage, color = `Node Type`)) +
    geom_line() +
    geom_point() + 
    theme_minimal() + 
    theme(axis.title = element_blank()) + 
    scale_x_date(date_labels = "%b %y")

ggplotly(nested_storage_fig)
```

### Specific nodes above cap

```{r, warning=FALSE, echo=FALSE}
by_node_storage %>% 
        ungroup() %>%
        filter(target_is_public == FALSE & gig_tot_size >= 5) %>% 
        select(target_guid, gig_tot_size) %>% 
        arrange(desc(gig_tot_size)) %>%
  datatable(colnames = c('Node GUID', 'Storage in GB'),
            caption = 'Private nodes above limit',
            extensions = 'Buttons',  
            options = list(dom = 'Bfrtip', buttons = list( list(extend = 'collection', buttons = list(list(extend='csv',filename='reg_form_counts.csv'),
                                                                 list(extend='excel', filename = 'reg_form_counts.xlsx') ),text="Download"))))
```

\
\

```{r, warning=FALSE, echo=FALSE}
by_node_storage %>% 
        ungroup() %>%
        filter(target_is_public == TRUE & gig_tot_size >= 50) %>% 
        select(target_guid, gig_tot_size) %>% 
        arrange(desc(gig_tot_size)) %>%
  datatable(colnames = c('Node GUID', 'Storage in GB'),
            caption = 'Public nodes at limit',
            extensions = 'Buttons',  
            options = list(dom = 'Bfrtip', buttons = list( list(extend = 'collection', buttons = list(list(extend='csv',filename='reg_form_counts.csv'),
                                                                 list(extend='excel', filename = 'reg_form_counts.xlsx') ),text="Download"))))
```




