---
title: "User Generation By Product"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    theme: bootstrap
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(gt)
library(here)
library(highcharter)
library(dichromat)
library(DT)
library(kableExtra)
library(knitr)

user_generation_data <- read_csv(here::here('data_for_mockup.csv'))

cols <- c('#34495D', '#3277A2', '#14A4EB', '#A8C8DD')
```


Monthly Increases
===================================== 

Column {data-width=200}
-----------------------------------------------------------------------

### Users Definitions

* ***New sign-ups***: Counts users who clicked the 'sign-up' button on specific pages

* ***New invites***: Counts the number of unregistered contributors who were added to a new product.

* ***New claims***: Counts unregistered contributors who claimed their account & which product they claimed it from.

### Product Definitions

* ***Registries***: Includes OSFRegistries and Pre-reg and ERP campaign pages

* ***Preprints***: Includes OSFPreprints and all branded preprint pages.

* ***OSF4M***: Anyone who created an account by emailing in an osf4m talk/poster.

* ***OSF***: Everyone else [OSF pages, collections, instituional pages, & SSO]

Column {data-width=500}
-----------------------------------------------------------------------

### Last Quarter's New Users {data-height=500}

```{r}
quarterly_numbers <- user_generation_data %>%
                        group_by(product, user_type) %>%
                        slice(1L) %>%
                        ungroup() %>%
                        select(-date, -sso_users) %>%
                        pivot_wider(names_from = user_type, values_from = new_n)

sso_percentages <- user_generation_data %>%
                        group_by(product, user_type) %>%
                        slice(1L) %>%
                        ungroup() %>%
                        mutate(user_type_ssoprc = paste0(round(100 *sso_users/new_n,2), '%')) %>%
                        select(-date, -new_n, -sso_users) %>%
                        pivot_wider(names_from = user_type, values_from = user_type_ssoprc)

rbind(quarterly_numbers, sso_percentages) %>%
    rename(` ` = 'product',
           `New Signed-Ups` = 'new_active',
           `New Invites` = 'nonreg_added',
           `New claims` = 'nonreg_claimed') %>%
    kable(align = 'c') %>%
    kable_styling('striped', full_width = F) %>%
    pack_rows('Raw Counts', 1, 4) %>%
    pack_rows('SSO perc', 5, 8)
```

### New unregistered contributor invitations {data-height=500}

```{r}
user_generation_data %>%
  filter(user_type == 'nonreg_added') %>%
  hchart(., type = 'line',
         hcaes(x = date,
               y = new_n,
               group = product)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```




Column {data-width=500}
-----------------------------------------------------------------------
### New direct user sign-ups {data-height=500}

```{r}
user_generation_data %>%
  filter(user_type == 'new_active') %>%
  hchart(., type = 'line',
         hcaes(x = date,
               y = new_n,
               group = product)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```

### New unregistered accounts claimed {data-height=500}

```{r}
user_generation_data %>%
  filter(user_type == 'nonreg_claimed') %>%
  hchart(., type = 'line',
         hcaes(x = date,
               y = new_n,
               group = product)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```


Cumulative Totals
===================================== 

Column {data-width=200}
-----------------------------------------------------------------------

### Users Definitions

* ***New sign-ups***: Counts users who clicked the 'sign-up' button on specific pages

* ***New invites***: Counts the number of unregistered contributors who were added to a new product.

* ***New claims***: Counts unregistered contributors who claimed their account & which product they claimed it from.

### Product Definitions

* ***Registries***: Includes OSFRegistries and Pre-reg and ERP campaign pages

* ***Preprints***: Includes OSFPreprints and all branded preprint pages.

* ***OSF4M***: Anyone who created an account by emailing in an osf4m talk/poster.

* ***OSF***: Everyone else [OSF pages, collections, instituional pages, & SSO]


Column {data-width = 500}
-----------------------------------------------------------------------

### Cumulative Total Table {data-height=500}

```{r}
quarterly_numbers <- user_generation_data %>%
                        group_by(product, user_type) %>%
                        slice(1L) %>%
                        ungroup() %>%
                        select(-date, -sso_users) %>%
                        pivot_wider(names_from = user_type, values_from = new_n)

sso_percentages <- user_generation_data %>%
                        group_by(product, user_type) %>%
                        slice(1L) %>%
                        ungroup() %>%
                        mutate(user_type_ssoprc = paste0(round(100 *sso_users/new_n,2), '%')) %>%
                        select(-date, -new_n, -sso_users) %>%
                        pivot_wider(names_from = user_type, values_from = user_type_ssoprc)

rbind(quarterly_numbers, sso_percentages) %>%
    rename(` ` = 'product',
           `New Signed-Ups` = 'new_active',
           `New Invites` = 'nonreg_added',
           `New claims` = 'nonreg_claimed') %>%
    kable(align = 'c') %>%
    kable_styling('striped', full_width = F) %>%
    pack_rows('Raw Counts', 1, 4) %>%
    pack_rows('SSO perc', 5, 8)
```


### Cumulative unregistered contributor invitations {data-height=500}

```{r}
user_generation_data %>%
  filter(user_type == 'nonreg_added') %>%
  hchart(., type = 'line',
         hcaes(x = date,
               y = new_n,
               group = product)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```


Column {data-width = 500}
-----------------------------------------------------------------------

### Cumulative direct user sign-ups {data-height=500}

```{r}
user_generation_data %>%
  filter(user_type == 'new_active') %>%
  hchart(., type = 'line',
         hcaes(x = date,
               y = new_n,
               group = product)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```

### Cumulative unregistered accounts claimed {data-height=500}

```{r}
user_generation_data %>%
  filter(user_type == 'nonreg_claimed') %>%
  hchart(., type = 'line',
         hcaes(x = date,
               y = new_n,
               group = product)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```

