---
title: "User Generation By Product"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    theme: bootstrap
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(gt)
library(here)
library(highcharter)
library(dichromat)
library(DT)
library(kableExtra)
library(knitr)
library(lubridate)

user_generation_data <- read_csv(here::here('full_hist_cat_date.csv')) %>%
                            mutate(month = as.Date(month))

cols <- c('#34495D', '#3277A2', '#14A4EB', '#A8C8DD')
```


Monthly Increases
===================================== 

Column {data-width=200}
-----------------------------------------------------------------------

### Users Definitions

* ***New sign-ups***: Counts users who clicked the 'sign-up' button on specific pages

* ***New invites***: Counts the number of unregistered contributors who were added to a new product.

* ***New claims***: Counts unregistered contributors who claimed their account & which product they claimed it from.

### Product Definitions

* ***Registries***: Includes OSFRegistries and Pre-reg and ERP campaign pages

* ***Preprints***: Includes OSFPreprints and all branded preprint pages.

* ***OSF4M***: Anyone who created an account by emailing in an osf4m talk/poster.

* ***OSF***: Everyone else [OSF pages, collections, instituional pages, & SSO]

Column {data-width=500}
-----------------------------------------------------------------------

### Last Quarter's New Users {data-height=500}

```{r}
quarterly_numbers <- user_generation_data %>%
                        arrange(desc(month)) %>%
                        group_by(product_type) %>%
                        slice_head(n = 3) %>%
                        summarize(new_signups = sum(new_signups), new_invitees = sum(new_invitees), new_claims = sum(new_claims))

sso_percentages <- user_generation_data %>%
                        arrange(desc(month)) %>%
                        group_by(product_type) %>%
                        slice_head(n = 3) %>%
                        select(-starts_with('cum')) %>%
                        summarise(across(where(is.numeric), sum)) %>%
                        ungroup() %>%
                        mutate(newsignups_ssoprc = paste0(round(100 *sso_newsignups/new_signups,2), '%'),
                               newsources_ssoprc = 'NA',
                               new_claims_ssoprc = paste0(round(100 *sso_newclaims/new_claims,2), '%')) %>%
                        select(product_type, ends_with('ssoprc')) %>%
                        rename(new_signups = newsignups_ssoprc,
                               new_invitees = newsources_ssoprc,
                               new_claims = new_claims_ssoprc)

rbind(quarterly_numbers, sso_percentages) %>%
    rename(` ` = 'product_type',
           `New Signed-Ups` = 'new_signups',
           `New Invites` = 'new_invitees',
           `New claims` = 'new_claims') %>%
    kable(align = 'c') %>%
    kable_styling('striped', full_width = F) %>%
    pack_rows('Raw Counts', 1, 4) %>%
    pack_rows('SSO perc', 5, 8)
```

### New unregistered contributor invitations {data-height=500}

```{r}
user_generation_data %>%
  filter(month >= '2020-05-01') %>%
  hchart(., type = 'line',
         hcaes(x = month,
               y = new_invitees,
               group = product_type)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```




Column {data-width=500}
-----------------------------------------------------------------------
### New direct user sign-ups {data-height=500}

```{r}
user_generation_data %>%
  hchart(., type = 'line',
         hcaes(x = month,
               y = new_signups,
               group = product_type)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```

### New unregistered accounts claimed {data-height=500}

```{r}
user_generation_data %>%
  filter(month >= '2020-05-01') %>%
  hchart(., type = 'line',
         hcaes(x = month,
               y = new_claims,
               group = product_type)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```


Percentage Monthly Increase
===================================== 

Column {data-width=200}
-----------------------------------------------------------------------

### Users Definitions

* ***New sign-ups***: Counts users who clicked the 'sign-up' button on specific pages

* ***New invites***: Counts the number of unregistered contributors who were added to a new product.

* ***New claims***: Counts unregistered contributors who claimed their account & which product they claimed it from.

### Product Definitions

* ***Registries***: Includes OSFRegistries and Pre-reg and ERP campaign pages

* ***Preprints***: Includes OSFPreprints and all branded preprint pages.

* ***OSF4M***: Anyone who created an account by emailing in an osf4m talk/poster.

* ***OSF***: Everyone else [OSF pages, collections, instituional pages, & SSO]


Column {data-width = 500}
-----------------------------------------------------------------------

### Percentage Quarterly User Generation {data-height=500}

```{r}
perc_numbers <- quarterly_numbers %>% 
                  mutate(across(where(is.numeric), ~paste0(round(100 *./sum(.),2),'%')))


perc_numbers %>%
    rename(` ` = 'product_type',
           `New Signed-Ups` = 'new_signups',
           `New Invites` = 'new_invitees',
           `New Claims` = 'new_claims') %>%
    kable(align = 'c') %>%
    kable_styling('striped', full_width = F)
```


### Cumulative unregistered contributor invitations {data-height=500}

```{r}
user_generation_data %>%
  hchart(., type = 'line',
         hcaes(x = month,
               y = cum_new_sources,
               group = product_type)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```


Column {data-width = 500}
-----------------------------------------------------------------------

### Cumulative direct user sign-ups {data-height=500}

```{r}
user_generation_data %>%
  hchart(., type = 'line',
         hcaes(x = month,
               y = cum_new_signups,
               group = product_type)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```

### Cumulative unregistered accounts claimed {data-height=500}

```{r}
user_generation_data %>%
  filter(month >= '2020-05-01') %>%
  hchart(., type = 'line',
         hcaes(x = month,
               y = cum_new_claims,
               group = product_type)) %>%
  hc_tooltip(table = TRUE, sort = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_xAxis(title = list(text = ""), tickInterval = 86400000 * 30) %>% #tick interval for date in milliseconds
  hc_yAxis(title = list(text = "Number of Users")) %>%
  hc_colors(cols) %>%
  hc_exporting(
    enabled = TRUE, filename="newuser_generation", 
              formAttributes=list(target="_blank"),
               buttons=list(contextButton=list(
               text="Export", theme=list(fill="transparent"))))
```

